---
title: "GIS-South-Thompson"
author: "Patrick Zubick"
date: "2023-03-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## here we will acquire the basemaps and CU boundary shapefiles for the GIS work we are doing with Simon.

## first need to get my packages of interest and most use

```{r}
library(tidyverse)
library(raster)
library(RCurl)
library(sf)
library(maps) 
library(mapdata)
library(maptools)
library(rgeos)
library(rgdal)
library(ggplot2)
library(ggsn)
library(tidyverse)
library(here)
library(ggmap)
library(cowplot)
library(ggpubr)

# dont think I will need more packages but can add more if need be

```

```{r}

# can i visualize the chinook shapefile

# Read in the shapefiles for my species of interest... CHinook, Coho and Sockeye...

shapefile.coho <- st_read("CO_CU_BOUNDARY_EN.shp")


shapefile.chinook <- st_read("CK_CU_BOUNDARY_EN.shp")


shapefile.sox <- st_read("SEL_CU_BOUNDARY_En.shp")


# all shapefiles seem good, need a base map to overlay on and see whats up....

# pull in basemap shapefile...

bc <- st_read("land.shp", quiet = TRUE)
plot(bc)

# Define the bounding box
bbox <- st_bbox(c(xmin = -124, ymin = 48, xmax = -114, ymax = 53), crs = st_crs(bc))

# Crop the shapefile to the bounding box
bc_cropped <- st_crop(bc, bbox)

plot(shapefile.chinook)

ggplot() + 
  geom_sf(data = bc) + 
  geom_sf(data = shapefile.chinook)
      
str(bc)
st_crs(bc) # WGS 84
# transform to UTMs
bcUTM <- st_transform(bc, crs = 3157) # 3157 is the CRS for UTM zone 10

str(shapefile.chinook)
st_crs(shapefile.chinook) # WGS 84
# transform to UTMs

chinookUTM <- st_transform(shapefile.chinook, crs = 3157) # 3157 is the CRS for UTM zone 10
str(chinookUTM)
st_crs(chinookUTM) # WGS 84
# transform to UTMs

plot(bc)

ggplot() + 
geom_sf(data = bcUTM) +
   geom_sf(data = chinookUTM)

   
# not exascly what we want... does not quite line up... neeed to get them both on the same coord system.. 

st_crs(bc)
st_crs(shapefile.chinook)

# i think I should swithc to all using the chinook coord system so will try that next time.. 
shapefile.chinook <- st_transform(shapefile.chinook, crs = st_crs(bc))


# Plot the maps
ggplot() + 
  geom_sf(data = bc) + 
  geom_sf(data = shapefile.chinook) +
  coord_sf(crs = st_crs(bc))

# if i make changes here can I commit to git?

# wahta baout now

```
```{r}
# try with new shape file from the workshop..

# rnaturalearth
north.america <- rnaturalearth::ne_countries(scale = "large", continent = "north america",
                                             returnclass = "sf")

shapefile.coho <- st_read("CO_CU_BOUNDARY_EN.shp")
shapefile.coho

shapefile.chinook <- st_read("CK_CU_BOUNDARY_EN.shp")
shapefile.chinook

shapefile.sox <- st_read("SEL_CU_BOUNDARY_En.shp")
shapefile.sox

str(north.america)
st_crs(north.america) # WGS 84

str(shapefile.chinook)
st_crs(shapefile.chinook) # WGS 8

# transform to UTMs
bcUTM <- st_transform(north.america, crs = 3157) # 3157 is the CRS for UTM zone 10
chinookUTM <- st_transform(shapefile.chinook, crs = 3157) # 3157 is the CRS for UTM zone 10
cohoUTM <- st_transform(shapefile.coho, crs = 3157) # 3157 is the CRS for UTM zone 10
sockeyeUTM <- st_transform(shapefile.sox, crs = 3157) # 3157 is the CRS for UTM zone 10



# try to add CU

ggplot() + 
geom_sf(data = bcUTM) +
   geom_sf(data = chinookUTM)


# map

# convert UTM eastings and northings from metres into kilometres for all shapefiles
bcUTM$geometry <- bcUTM$geometry/1000
chinookUTM$geometry <- chinookUTM$geometry/1000
cohoUTM$geometry <- cohoUTM$geometry/1000
sockeyeUTM$geometry <- sockeyeUTM$geometry/1000


# map
ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = chinookUTM ,  aes(fill = CU_NAME), show.legend = FALSE)+
  scale_x_continuous(limits = c(600, 1100), breaks = c(600, 850, 1100)) +
  scale_y_continuous(limits = c(5450, 5650), breaks = c(5300, 5400, 5500, 5600)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

# that looks unreal, need to select out the CU i Want to include in my map....

# and then subesquently in the file I will send to simon....


```

# snip out CU of interest in south thompson 


```{r}

# i have my UTM shapefiles for each CU, chinookUTM, sockeyeUTM, cohoUTM
# need to know the namesI need.. str$CU_NAME

# need to keep these ones... "Shuswap River_SU_0.3" ,"South Thompson_SU_0.3" ,"Upper Adams River_SU_x.x", "Lower Thompson_SP_1.2" , "South Thompson-Bessette Creek_SU_1.2", "South Thompson_SU_1.3"   


# Create a vector of the polygon names you want to keep --> need to know the names of my polygons...
chinook.CU <- c("Shuswap River_SU_0.3" ,"South Thompson_SU_0.3" ,"Upper Adams River_SU_x.x", "Lower Thompson_SP_1.2" , "South Thompson-Bessette Creek_SU_1.2", "South Thompson_SU_1.3"   )

# Subset the shapefile based on the polygon names
chinook.CU.polygons <- subset(chinookUTM, CU_NAME %in% chinook.CU)

# Write the subsetted shapefile to a new file
##st_write(chinook.CU.polygons, "chinook.CU.ST.shp")

# should work tho which is nice...

# lets see how this looks in a map??

# map just BC

ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = chinook.CU.polygons,  aes(fill = CU_NAME))+scale_x_continuous(limits = c(0, 2000)) +
  scale_y_continuous(limits = c(5000, 6000)) +
  theme_bw()

# smaller area mappppp
ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = chinook.CU.polygons,  aes(fill = CU_NAME))+scale_x_continuous(limits = c(500, 1000)) +
  scale_y_continuous(limits = c(5400, 5800)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

# that looks awesome, lets replicate the sucess with the other CU for sockeye and coho


# coho now... 
# just plot a bc map with coho to see how it looks and ensure it looks fine..


ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = cohoUTM,  aes(fill = CU_NAME), show.legend = FALSE)+scale_x_continuous(limits = c(0, 2000)) +
  scale_y_continuous(limits = c(5000, 6000)) +
  theme_bw()

# perfect, now need to select out my CU of interest for coho

(cohoUTM$CU_NAME)

# need "Lower Thompson" ,"South Thompson" 

# Create a vector of the polygon names you want to keep --> need to know the names of my polygons...
coho.CU <- c("Lower Thompson" ,"South Thompson")

# Subset the shapefile based on the polygon names
coho.CU.polygons <- subset(cohoUTM, CU_NAME %in% coho.CU)

# Write the subsetted shapefile to a new file
##st_write(coho.CU.polygons, "coho.CU.ST.shp")

# map just BC

ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = coho.CU.polygons,  aes(fill = CU_NAME))+scale_x_continuous(limits = c(0, 2000)) +
  scale_y_continuous(limits = c(5000, 6000)) +
  theme_bw()



# smaller area mappppp


ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = coho.CU.polygons,  aes(fill = CU_NAME))+scale_x_continuous(limits = c(500, 1000)) +
  scale_y_continuous(limits = c(5400, 5800)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

# perfect lets go to the sockeye world


# just plot a bc map with sockeye to see how it looks and ensure it looks fine..


ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = sockeyeUTM,  aes(fill = CU_NAME), show.legend = FALSE)+scale_x_continuous(limits = c(0, 2000)) +
  scale_y_continuous(limits = c(5000, 6000)) +
  theme_bw()

# that looks fine but it really omits the rivers+spawning areas looks like the CU are based on rearing lakes...

# perfect, now need to select out my CU of interest for sockeye

(sockeyeUTM$CU_NAME)

# need "Shuswap Complex-Late Timing",  "Kamloops-Early Summer Timing", "Shuswap Complex-Early Summer Timing, "(p)Adams and Momich Lakes-Early Summer Timing"

# Create a vector of the polygon names you want to keep --> need to know the names of my polygons...
sockeye.CU <- c("Shuswap Complex-Late Timing",  "Kamloops-Early Summer Timing", "Shuswap Complex-Early Summer Timing", "(p)Adams and Momich Lakes-Early Summer Timing")

# Subset the shapefile based on the polygon names
sockeye.CU.polygons <- subset(sockeyeUTM, CU_NAME %in% sockeye.CU)

# Write the subsetted shapefile to a new file
##st_write(sockeye.CU.polygons, "sockeye.CU.ST.shp")

# map just BC

ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = sockeye.CU.polygons,  aes(fill = CU_NAME))+scale_x_continuous(limits = c(0, 2000)) +
  scale_y_continuous(limits = c(5000, 6000)) +
  theme_bw()

# smaller area mappppp

ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = sockeye.CU.polygons,  aes(fill = CU_NAME))+scale_x_continuous(limits = c(500, 1000)) +
  scale_y_continuous(limits = c(5400, 5800)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

# i do not really know how to compartmentalize that but oh whale....because the CU are clearly by rearing lakes...

# lets see if I can drop all my CU on one map?!?!?!

# likley best to put on 3 adjoining maps but I am feeling crazy...

# smaller area mappppp

ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = sockeye.CU.polygons,  aes(fill = CU_NAME))  + geom_sf(data = coho.CU.polygons,  aes(fill = CU_NAME))  + geom_sf(data = chinook.CU.polygons,  aes(fill = CU_NAME))+scale_x_continuous(limits = c(500, 1000)) +
  scale_y_continuous(limits = c(5400, 5800)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())



# i suppose thats okay..should probs put them side by side...with no legend..

sockeye.cu.st = ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = sockeye.CU.polygons,  aes(fill = CU_NAME), show.legend = FALSE)+scale_x_continuous(limits = c(500, 1000)) +
  scale_y_continuous(limits = c(5400, 5800)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

coho.cu.st = ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = coho.CU.polygons,  aes(fill = CU_NAME), show.legend = FALSE)+scale_x_continuous(limits = c(500, 1000)) +
  scale_y_continuous(limits = c(5400, 5800)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

chinook.cu.st = ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = chinook.CU.polygons,  aes(fill = CU_NAME), show.legend = FALSE)+scale_x_continuous(limits = c(500, 1000)) +
  scale_y_continuous(limits = c(5400, 5800)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

# Arrange the plots side by side

plot_grid(chinook.cu.st, coho.cu.st, sockeye.cu.st, ncol = 3)

ggarrange(chinook.cu.st, coho.cu.st, sockeye.cu.st, ncol = 3, labels = c("Chinook CU", "Coho CU", "Sockeye CU"))

# try one more thing then carry on and probs send simon the information...

sockeye.cu.st = ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = sockeye.CU.polygons,  aes(fill = CU_NAME), show.legend = TRUE)+scale_x_continuous(limits = c(500, 1000)) +
  scale_y_continuous(limits = c(5400, 5800)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

coho.cu.st = ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = coho.CU.polygons,  aes(fill = CU_NAME), show.legend = TRUE)+scale_x_continuous(limits = c(500, 1000)) +
  scale_y_continuous(limits = c(5400, 5800)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

chinook.cu.st = ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = chinook.CU.polygons,  aes(fill = CU_NAME), show.legend = TRUE)+scale_x_continuous(limits = c(500, 1000)) +
  scale_y_continuous(limits = c(5400, 5800)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

# Arrange the plots side by side

plot_grid(chinook.cu.st, coho.cu.st, sockeye.cu.st, ncol = 3)

ggarrange(chinook.cu.st, coho.cu.st, sockeye.cu.st, ncol = 3, labels = c("Chinook CU", "Coho CU", "Sockeye CU") ,common.legend = TRUE,legend = "bottom", widths = c(0.3, 0.3, 0.3),heights = c(0.5, 0.5, 0.2))

# try one more thing then carry on and probs send simon the information...

# going to leave as is i think...

# would be nice to overlay stream network... but that can wait... 

# lets see the sockeye lines... need to set coord system and all that jazzzzz...

shapefile.sox.lines <- readOGR(dsn = "C:/Users/patch/OneDrive/Desktop/MSc-Culvert/GIS-Analysis/GIS-South-Thompson-Culverts", layer = "sockeye.spawning_lines_fraser")

# Convert SpatialLinesDataFrame object to sf object
shapefile.sox.lines.UTM_sf <- st_as_sf(shapefile.sox.lines)

shapefile.sox.lines<- st_transform(shapefile.sox.lines.UTM_sf, crs = 3157) # 3157 is the CRS for UTM zone 10
str(shapefile.sox.lines)

# convert UTM eastings and northings from metres into kilometres for all shapefiles
shapefile.sox.lines$geometry <- shapefile.sox.lines$geometry/1000


# Plot lines as solid, and then zoom in... 
ggplot() + 
  geom_sf(data = bcUTM) +
  geom_sf(data = shapefile.sox.lines)


# zoom in.. 
sockeye.lines.cu.st = ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = shapefile.sox.lines,  aes(fill = Species), show.legend = TRUE)+scale_x_continuous(limits = c(500, 1000)) +
  scale_y_continuous(limits = c(5400, 5800)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

sockeye.lines.cu.st

# i just want sockeye lake type... 

str(shapefile.sox.lines)

unique(shapefile.sox.lines$Species)


# Create a vector of the polygon names you want to keep --> need to know the names of my polygons...
sockeye.lines.CU <- c("river sockeye")

# Subset the shapefile based on the polygon names
sockeye.CU.lines <- subset(shapefile.sox.lines, Species %in% sockeye.lines.CU)

# Write the subsetted shapefile to a new file
##st_write(sockeye.CU.lines, "sockeye.lines.CU.ST.shp")

# zoom in.. 
sockeye.lines.cu.st = ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = sockeye.CU.lines,  aes(fill = Species), show.legend = TRUE)+scale_x_continuous(limits = c(500, 1000)) +
  scale_y_continuous(limits = c(5400, 5800)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

sockeye.lines.cu.st

# add this to the CU map..

 ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = sockeye.CU.polygons)+geom_sf(data = sockeye.CU.lines,  aes(fill = Species), show.legend = TRUE)+scale_x_continuous(limits = c(500, 1000)) +
  scale_y_continuous(limits = c(5400, 5800)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())



# add this to the CU map..

 # looks okay can cut it out if need be i suppose...

 
 
watershed.bc <- readOGR(dsn = "C:/Users/patch/OneDrive/Desktop/MSc-Culvert/GIS-Analysis/GIS-South-Thompson-Culverts/FWA_NAMED_WATERSHEDS_POLY", layer = "FWNMDWTRSH_polygon")


str(watershed.bc)

# Convert SpatialLinesDataFrame object to sf object
watershed.bc.sf <- st_as_sf(watershed.bc)

watershed.bc.sf.UTM<- st_transform(watershed.bc.sf, crs = 3157) # 3157 is the CRS for UTM zone 10

# convert UTM eastings and northings from metres into kilometres for all shapefiles
watershed.bc.sf.UTM$geometry <- watershed.bc.sf.UTM$geometry/1000

# put it on a map of BC
str(watershed.bc.sf)

ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = watershed.bc.sf.UTM,  aes(fill = GNIS_NAME))+scale_x_continuous(limits = c(0, 2000)) +
  scale_y_continuous(limits = c(5000, 6000)) +
  theme_bw()

# select out the watershed i want South Thompson River

# Create a vector of the polygon names you want to keep --> need to know the names of my polygons...
souththompson.poly <- c("South Thompson River")

# Subset the shapefile based on the polygon names
south.thompson.poly <- subset(watershed.bc.sf.UTM, GNIS_NAME %in% souththompson.poly)

# Write the subsetted shapefile to a new file
st_write(south.thompson.poly, "south.thompson.shp")

# zoomed in area

ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = south.thompson.poly,  aes(fill = GNIS_NAME))+scale_x_continuous(limits = c(0, 2000)) +
  scale_y_continuous(limits = c(5000, 6000)) +
  theme_bw()


# mess around by adding the watershed boundary with the CU... 

ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = south.thompson.poly) + geom_sf(data = sockeye.CU.polygons,  aes(fill = CU_NAME), show.legend = TRUE)+scale_x_continuous(limits = c(500, 1000)) +
  scale_y_continuous(limits = c(5400, 5800)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = south.thompson.poly) + geom_sf(data = coho.CU.polygons,  aes(fill = CU_NAME), show.legend = TRUE)+scale_x_continuous(limits = c(500, 1000)) +
  scale_y_continuous(limits = c(5400, 5800)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

ggplot() + geom_sf(data = bcUTM, col = "black", fill = "grey75", lwd = 0.01) + geom_sf(data = south.thompson.poly) + geom_sf(data = chinook.CU.polygons,  aes(fill = CU_NAME), show.legend = TRUE)+scale_x_continuous(limits = c(500, 1000)) +
  scale_y_continuous(limits = c(5400, 5800)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

# Arrange the plots side by side

plot_grid(chinook.cu.st, coho.cu.st, sockeye.cu.st, ncol = 3)

ggarrange(chinook.cu.st, coho.cu.st, sockeye.cu.st, ncol = 3, labels = c("Chinook CU", "Coho CU", "Sockeye CU") ,common.legend = TRUE,legend = "bottom", widths = c(0.3, 0.3, 0.3),heights = c(0.5, 0.5, 0.2))

#can probably do a snip of the watershed outside the south thompson... need to cut the sockeye coho and chinook ones...



```

# want to buiild a map of our study area, thjat includes streams, CU for chinook, sockeye and coho, and overlays a gradient of barrier counts? or stream crossings in general? coudl be a nice visualization overlay watershed units from freshwater atlas... 

```{r}

```

## build map of study area, just sites as dots, over basemap with some major streams for context... 


```{r}
# lets try to do this myself...cause stupid gpt cant sort it out lolll  

bc <- bc_bound()

plot(st_geometry(bc))

water5M = watercourses_5M()


# add sites in... 

Compliance_Study_Sites <- read_csv("C:/Users/patch/OneDrive/Desktop/MSc-Culvert/MSc-R-Git-CODING/MSc_Compliance_RStudio/Compliance-Study-Sites.csv")

# need to clean up df by removing the doubles @ fortune, campbell

Compliance_Study_Sites$Site <- ifelse(Compliance_Study_Sites$Site %in% c("DFO 2A", "DFO 2B"),
                                      gsub("DFO 2A|DFO 2B", "DFO 2", Compliance_Study_Sites$Site),
                                      Compliance_Study_Sites$Site)

Compliance_Study_Sites$Site <- ifelse(Compliance_Study_Sites$Site %in% c("DFO 24A", "DFO 24B"),
                                      gsub("DFO 24A|DFO 24B", "DFO 24", Compliance_Study_Sites$Site),
                                      Compliance_Study_Sites$Site)

Compliance_Study_Sites$Site <- ifelse(Compliance_Study_Sites$Site %in% c("DFO 4A", "DFO 4B"),
                                      gsub("DFO 4A|DFO 4B", "DFO 4", Compliance_Study_Sites$Site),
                                      Compliance_Study_Sites$Site)

compliance.sites.clean = unique(Compliance_Study_Sites)


#Convert the compliance.sites.clean data frame to an sf object
compliance_sf <- st_as_sf(compliance.sites.clean, coords = c("Long", "Lat"), crs = 4326)

# Transform the coordinates to BC Albers (EPSG code 3005)
compliance_sf_transformed <- st_transform(compliance_sf, 3005)


# Convert the compliance.sites.clean data frame to an sf object
compliance_sf <- st_as_sf(compliance.sites.clean, coords = c("Long", "Lat"), crs = 4326)

# Transform the coordinates to BC Albers (EPSG code 3005)
compliance_sf_transformed <- st_transform(compliance_sf, 3005)

# reproject compliance_sf_transformed to UTM
compliance_sf_transformed <- st_transform(compliance_sf_transformed, 32610)

# create a bounding box around the points in compliance_sf_transformed
bbox <- st_bbox(compliance_sf_transformed)

# crop bc to the extent of the buffered bounding box

# convert bbox to sf object and buffer it
bbox_sf <- st_as_sfc(bbox)
bbox_sf_buffered <- st_buffer(bbox_sf, dist = 10000)

# need to set to the same crs
# Ensure that the spatial reference systems match
bbox_sf_buffered <- st_transform(bbox_sf_buffered, st_crs(bc))

bc_cropped <- st_crop(bc, bbox_sf_buffered)
bc_water_cropped <- st_crop(water5M, bc_cropped)

plot(bc_water_cropped)

# need to plot the basemap... 


# Create the basemap
bc_map <- ggplot() +
  geom_sf(data = bc, fill = "grey85", col = "black", lwd = 0.1) +
  coord_sf(datum = NA) + geom_sf(data = watercourses_5M()) +
  geom_sf(data = bbox_sf_buffered, fill = NA, color = "red", size = 1.5)+
  theme_classic()

bc_map

# try to plot the bc cropped

# Create the main map with some stream lines... Probs want majr lakes in bc too...

bc_map_cropped <- ggplot() +
  geom_sf(data = bc_cropped, fill = "grey85", col = "black", lwd = 0.1) +
  coord_sf(datum = NA) +
  geom_sf(data = compliance_sf_transformed, aes(color = remediation_class)) +
  scale_colour_manual(values = c("#ff6700", "#c15ccb", "#057076"))+geom_sf(data = bc_water_cropped, col = "lightblue") +
  theme_classic() +
  theme(legend.position = "none") # remove legend

bc_map_cropped

# looking good so far... 

# i want to have this plot surrounded by  a balck outline rectangle..

str(bc_map_cropped)

# try to add them together 


# Arrange the maps together
ggarrange(
  bc_map_cropped + theme_void(),  # Main map with no background
  bc_map + theme_void(),          # Inset map with no background
  widths = c(4, 1),               # Set the width ratio between the maps
  heights = c(3, 1),              # Set the height ratio between the maps
  ncol = 2,                       # Arrange the maps in two columns
  nrow = 2,                       # Arrange the maps in two rows
  left = "50%",                    # Shift the inset map to the left
  top = "50%",                     # Shift the inset map to the top
  bottom = "50%",                 # Shrink the height of the main map to make room for the inset map
  legend = "none"                 # Remove the legend from both maps
)




```

